Sound Automated Synthesis of Digital Controllers

### 2016-10-11 paper/paper.tex
Minor changes

%
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modeling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
\end{equation}
where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model. Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.

@@

In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$ and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the following equation may written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
\item the controller $\hat{C}(z)$ is a minimum-phase system. 
\end{itemize}
\end{mylemma}

>>>>

%
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modeling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\label{eq:complete_unc_model}
\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
\end{equation}
where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model. Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.

@@

In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation may be written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete-model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
\item the controller $\hat{C}(z)$ is a minimum-phase system. 
\end{itemize}
\end{mylemma}
